---
title: "basic_workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{basic_workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message=FALSE, warning=FALSE}
library(retractionfindr)
library(tidyverse)
```


Once you have your search (from Web of Science, PubMed, etc.), you can use `retractionfindr` functions to search for retractions. Export your search as a `.ris` file and use the `read_refs` function to read the file. Then use the `check_retracted` function to search for retractions.

This returns a list of the number of retractions and the total number of records in the file, as well as a dataframe with all the references and a column indicating whether the reference is retracted or not. 

```{r load the data}
# First you need to upload a RIS file
# We use the read_refs function from synthesisr to read the RIS file
refs<-synthesisr::read_refs(system.file("extdata", "example.ris", package = "retractionfindr"))

out<-check_retracted(refs)

out$n_total
out$n_retracted

```

You may wish to separate the retracted and non-retracted articles. You can do this using the `separate_retracted` function.

```{r separate the retracted articles}
sep_refs<-separate_retracted(out$refs)
sep_refs[1] # retracted 
#sep_refs[2] # non-retracted
```