---
title: "basic_workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{basic_workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message=FALSE, warning=FALSE}
library(retractionfindr)
library(synthesisr)
```

Once you have your search results (from Web of Science, PubMed, etc.), export them as a `.ris` file
and use `synthesisr::read_refs()` to load them into R. Then pass the resulting dataframe to
`check_retracted()` to flag any retracted articles.

```{r check-for-retractions}
refs <- synthesisr::read_refs(system.file("extdata", "example.ris", package = "retractionfindr"))

checked <- check_retracted(refs)
```

`check_retracted()` returns the original dataframe with three new columns added: `is_retracted`
(1 or 0), `retraction_nature` (e.g. "Retraction", "Expression of Concern"), and
`retraction_reason` (semicolon-separated reasons from RetractionWatch).

Use `count_retracted()` to get a quick summary:

```{r count-results}
count_retracted(checked)
```

To split the results into separate dataframes for retracted and non-retracted articles, use
`separate_retracted()`:

```{r separate-results}
sep <- separate_retracted(checked)

sep$retracted      # articles flagged as retracted
sep$non_retracted  # all others
```

Set `write_ris = TRUE` to also save the retracted articles as a `.ris` file:

```{r write-ris, eval=FALSE}
separate_retracted(checked, write_ris = TRUE, filename = "retracted", path = "output/")
```
